Preprocessing: trimming

### 2022-09-15 analysis/preprosessor/trimming.Rmd
finished trimming / moved files to preprosessor
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# KOT
```{r}
dt_kot <- dt_onset

# Offset 1 - Onset 2
dt_kot$KOT <- NA
for (row in 1:nrow(dt_kot)){
  if (row < nrow(dt_kot)){
    dt_kot$KOT[row+1] <- dt_offset$TimeStamp[row] - dt_onset$TimeStamp[row+1] # offset(n) - onset(n+1)
  }
}

@@

@@

# KV

# KV Difference

>>>>

# KOT

```{r, include = FALSE}
dt_kot <- dt_onset

# calculate KOT (Offset 1 - Onset 2)
dt_kot$KOT <- NA
for (row in 1:nrow(dt_kot)){
  if (row < nrow(dt_kot)){
    dt_kot$KOT[row+1] <- dt_offset$TimeStamp[row] - dt_onset$TimeStamp[row+1] # offset(n) - onset(n+1)
  }
}

@@

Remove `r nrow(dt_kot_subset)-nrow(dt_kot_trimmed)` responses beyond +- 3SD / `r 100*((nrow(dt_kot_subset)-nrow(dt_kot_trimmed))/nrow(dt_kot_subset))` % of total responses

@@

# KV
```{r, include = FALSE}
# calculate Diff (acceleration - velocity difference between notes)
dt_vel <- dt_onset
dt_vel$Diff <- diff(c(0, dt_vel$Velocity))

# remove the first note
dt_vel_diff <- dt_vel[RowNr != 1]
dt_vel$Diff <- NULL # remove Diff from dt_vel

# assign Subcomponents
# for each note
dt_vel$Articulation <- "NA"
dt_vel$Dynamics <- "NA"
# Legato/Forte
for (phrase in 1:length(ls_legato2)){
  for (note in 1:length(ls_legato2[[phrase]])){
    dt_vel[RowNr == ls_legato2[[phrase]][note]]$Articulation <- "Legato"
    dt_vel[RowNr  == ls_legato2[[phrase]][note]]$Dynamics <- "Forte"
  }
}
# Staccato/Piano
for (phrase in 1:length(ls_staccato2)){
  for (note in 1:length(ls_staccato2[[phrase]])){
    dt_vel[RowNr  == ls_staccato2[[phrase]][note]]$Articulation <- "Staccato"
    dt_vel[RowNr  == ls_staccato2[[phrase]][note]]$Dynamics <- "Piano"
  }
}
```

## Histogram
### Before removing outliers
```{r}
dt_vel_subset <- dt_vel[Articulation != "NA" & !is.na(Velocity)]

gghistogram(dt_vel_subset, x = "Velocity", color = "Articulation", bins = 150)
```

### After removing outliers
```{r}
vel_subcomponent <- dt_vel_subset[, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = Articulation]
dt_vel_trimmed <- data.table()
for (subcomponent in unique(dt_vel_subset$Articulation)){
  upper <- vel_subcomponent[Articulation == subcomponent]$Mean+3*vel_subcomponent[Articulation == subcomponent]$SD
  lower <- vel_subcomponent[Articulation == subcomponent]$Mean-3*vel_subcomponent[Articulation == subcomponent]$SD
  dt_current <- dt_vel_subset[Articulation == subcomponent & Velocity < upper & Velocity > lower]
  dt_vel_trimmed <- rbind(dt_vel_trimmed, dt_current)
}

gghistogram(dt_vel_trimmed, x = "Velocity", color = "Articulation", bins = 150)
```

Remove `r nrow(dt_vel_subset)-nrow(dt_vel_trimmed)` responses beyond +- 3SD / `r 100*((nrow(dt_vel_subset)-nrow(dt_vel_trimmed))/nrow(dt_vel_subset))` % of total responses

```{r, include = FALSE}
fwrite(dt_vel_trimmed, file = here("trimmed", "dt_vel_trimmed.txt"), row.names = F)
```

# KV Difference
```{r, include = FALSE}
# assign Interval
dt_vel_diff$Interval <- rep(1:71, nrow(dt_vel_diff)/71)

# assign Subcomponents
# for intervals
dt_vel_diff$Articulation <- "NA"
dt_vel_diff$Dynamics <- "NA"
# Legato/Forte
for (phrase in 1:length(ls_legato)){
  for (note in 1:length(ls_legato[[phrase]])){
    dt_vel_diff[Interval == ls_legato[[phrase]][note]]$Articulation <- "Legato"
    dt_vel_diff[Interval == ls_legato[[phrase]][note]]$Dynamics <- "Forte"
  }
}
# Staccato/Piano
for (phrase in 1:length(ls_staccato)){
  for (note in 1:length(ls_staccato[[phrase]])){
    dt_vel_diff[Interval == ls_staccato[[phrase]][note]]$Articulation <- "Staccato"
    dt_vel_diff[Interval == ls_staccato[[phrase]][note]]$Dynamics <- "Piano"
  }
}

# assign Subcomponent Change
for (number in change_1){
  dt_vel_diff[Interval == number]$Articulation <- "LtoS"
  dt_vel_diff[ Interval == number]$Dynamics <- "FtoP"
}
for (number in change_2){
  dt_vel_diff[Interval == number]$Articulation <- "StoL"
  dt_vel_diff[Interval == number]$Dynamics <- "PtoF"
}

```

## Histogram
### Before removing outliers
```{r}
dt_vel_diff_subset <- dt_vel_diff[Articulation != "NA" & !is.na(Diff)]

gghistogram(dt_vel_diff_subset, x = "Diff", color = "Articulation", bins = 150)
```

### After removing outliers
```{r}
vel_diff_subcomponent <- dt_vel_diff_subset[, .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = Articulation]
dt_vel_diff_trimmed <- data.table()
for (subcomponent in unique(dt_vel_diff_subset$Articulation)){
  upper <- vel_diff_subcomponent[Articulation == subcomponent]$Mean+3*vel_diff_subcomponent[Articulation == subcomponent]$SD
  lower <- vel_diff_subcomponent[Articulation == subcomponent]$Mean-3*vel_diff_subcomponent[Articulation == subcomponent]$SD
  dt_current <- dt_vel_diff_subset[Articulation == subcomponent & Diff < upper & Diff > lower]
  dt_vel_diff_trimmed <- rbind(dt_vel_diff_trimmed, dt_current)
}

gghistogram(dt_vel_diff_trimmed, x = "Diff", color = "Articulation", bins = 150)
```

Remove `r nrow(dt_vel_diff_subset)-nrow(dt_vel_diff_trimmed)` responses beyond +- 3SD / `r 100*((nrow(dt_vel_diff_subset)-nrow(dt_vel_diff_trimmed))/nrow(dt_vel_diff_subset))` % of total responses

```{r, include = FALSE}
fwrite(dt_vel_diff_trimmed, file = here("trimmed", "dt_vel_diff_trimmed.txt"), row.names = F)
```
